\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,
            total={7in, 9.9in},
            top=1in, left=0.2in]{geometry}

%%%%%%%%%%%%%%%%%%%%%%
%% COLOR
%%%%%%%%%%%%%%%%%%%%%%
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}

%%%%%%%%%%%%%%%%%%%%%%
%% HYPERREF
%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%
%% CURRVITA
%% ftp://ftp.dante.de/pub/tex/macros/latex/contrib/currvita/currvita.pdf
%%%%%%%%%%%%%%%%%%%%%%
% Define a command to generalize the font of the section indipendently from cvlist
\newcommand{\sectionfont}{\noindent \Large \scshape}
\usepackage[NoDate]{currvita}
\renewcommand{\cvheadingfont}{\LARGE\color{darkblue}}
\renewcommand{\cvlistheadingfont}{\sectionfont}
\renewcommand{\cvlabelfont}{\scshape}

%%%%%%%%%%%%%%%%%%%%%%
%% IFTHEN
%%%%%%%%%%%%%%%%%%%%%%
\usepackage{ifthen}
\newboolean{extended}
\setboolean{extended}{false}

% Disable page numbering
\pagenumbering{gobble}

\begin{document}
  \begin{cv}{\huge{Curriculum vit\ae~of \textsc{Filippo Squillace}}}
    \bigskip
    \bigskip
    \begin{minipage}[t]{0.7\textwidth}
      \begin{cvlist}{Professional experience}
        % Nov 2015 - current
        \item[\footnotesize{Nov 2015 - current}] \textbf{Software Development Engineer II at Amazon}\\
        \href{http://www.amazon.com}{Amazon}\hfill\textit{Dublin, IE}\\
        Additional roles: Tech leader, Solution Architect, Scrum Master
        \begin{small}
          \begin{itemize}
            \item Designed and implemented asynchronous APIs to manage the network monitoring micro-services.
            \item Designed and implemented the orchestration system that controls and distributes workload to the network micro-services.
          \end{itemize}
        \end{small}
        % Jan 14 2013 - Oct 2015
        \item[\footnotesize{Jan 2013 - Oct 2015}] \textbf{Software Development Engineer I at Amazon}\\
        \href{http://www.amazon.com}{Amazon}\hfill\textit{Dublin, IE}
        \begin{small}
          \begin{itemize}
            \item Designed and developed an asynchronous event based and highly scalable network monitoring system.
          \end{itemize}
        \end{small}
        % Aug-Sept 27 jun - 30 oct 2012
        \item[\footnotesize{Aug 2012 - Oct 2012}] \textbf{Software Developer in Django/Python}\\
        \href{http://opmservice.com}{Orloff Property Management}\hfill\textit{Berkeley, CA}
        \begin{small}
          \begin{itemize}
            \item Full stack web application for the property management of
            thousands of properties located in the states
            of California and Indiana.
            \ifthenelse{\boolean{extended}}{
              My tasks were to develop CRUD operations and
              more additional features such as generation of reports and
              filter/sort actions.
              The technology used was Django as Web Framework, JQuery to manage
              asynchronous request to the server. The deployment system used is
              Fabric in order to manage complex actions and ensure that the code
              has correctly deployed into the server. For testing the code it was
              used Selenium IDE and Selenium WebDriver test automation tool.
            }
          \end{itemize}
        \end{small}
        % Sept 2011 - Feb 2012
        \item[\footnotesize{Sep 2011 - Feb 2012}] \textbf{Researcher High Performance Computing}\\
        \href{http://www.inco2.upv.es/menu.php}{Interdisciplinary Computation and Communication Group}\hfill\textit{Valencia, ES}
        \begin{small}
          \begin{itemize}
            \item Optimized the computation of algorithms for solving
            the eigenvalue problem via graphics cards using CUDA.
            \ifthenelse{\boolean{extended}}{
              There are only few libraries that support
              the development of advanced algorithms in numerical linear algebra
              and some of them implement the main routines for linear algebra. It
              was necessary to develop projects to aim the improvement and
              integration of the existing libraries for graphics card
              programming. The Unit testing activity represented the main
              approach for the stability and precision of the algorithms.
              The Interdisciplinary Computation and Communication Group (INCO2-DSIC)
              is made up of researchers belonging to the Department of
              Information Systems and Computation (DSIC) of the Universidad
              Politécnica de Valencia.
           }
         \end{itemize}
        \end{small}
        %May 18 2009-- Aug 17 2009.
        \item[\footnotesize{May 2009 - Aug 2009}] \textbf{Java Analyst and Programmer}\\
        \href{http://www.zenitlab.it/}{ZENIT Information Systems}\hfill\textit{Cosenza, IT}
        \begin{small}
          \begin{itemize}
            \item Designed and developed the desktop client-side application for an Information System built via OpenSwing library and used Java EJB.
            \ifthenelse{\boolean{extended}}{
              The customer, Pubbliemme, is a leader for concession of advertising space in the center-south of Italy with over 2500 advertising establishments.
            }
          \end{itemize}
        \end{small}
      \end{cvlist}
      \begin{cvlist}{Education\footnotemark}
        \item[2010-2012] \textbf{M.Sc. in \href{http://www.dsic.upv.es/}{Parallel
    and Distributed Computing}}\\
        \href{http://www.upv.es/}{Polytechnic University of Valencia}\hfill\textit{Valencia, ES}\\
        \begin{tabular}{lp{5.0cm}}
          \textit{Final degree mark:} &  10 cum laude (out of 10) \\
          \ifthenelse{\boolean{extended}}{
            \textit{Thesis Topic:}      &  Optimization for the $\lambda$-modes
              computation (a generalized sparse eigenvalue problem) using CUDA\\
            \textit{Adviser:} & Prof. Vicente Vidal (\href{http://www.dsic.upv.es/}{DSIC Dep.})\\
            &  Prof. Gumersindo Verd\'{u} (Chemical and Nuclear Engineering Dep.)\\
            \textit{Main subjects:}     &  Linear Algebra, Numerical Computing,
              SPMD paradigm, Parallel/Distributed Computing, Computational Grids,
              Low-level programming, Optimization tools/techniques \\
          }
        \end{tabular}
        \ifthenelse{\boolean{extended}}{
          \hyperlink{mcpd}{\hfill | \footnotesize Detailed List of Exams}\\
        }
        \item[2007-2010] \textbf{M.Sc. in Computer Engineering}\\
        \href{http://www.unical.it/}{University of Calabria}\hfill\textit{Cosenza, IT}\\
        % Received Sep 27, 2010
        \begin{tabular}{lp{5cm}}
          \textit{Final degree mark:} &  110 (out of 110) cum laude\\
          \ifthenelse{\boolean{extended}}{
            \textit{Thesis Topic:}      &  Error correction and flow control
              techniques for reliable and efficient transmissions of multimedia
              contents in vehicular networks\\
            \textit{Adviser:}           &
              \href{http://wwwinfo.deis.unical.it/~fortino/}{Prof. Giancarlo
              Fortino} (\href{http://www.deis.unical.it}{DEIS Dep.})\\
            \textit{Main subjects:}     &  Data Mining, Artificial Intelligence,
              Software Engineer on Agent Systems, Reconfigurable Circuits (FPGA),
              Robotics, Distributed Systems, Computer Graphics, Vehicular
              Networks, Wireless Systems \\
          }
        \end{tabular}
        \ifthenelse{\boolean{extended}}{
          \hyperlink{iis}{\hfill | \footnotesize Detailed List of Exams} \\
        }

        \item[2004-2007] \textbf{B.Sc. in Computer Engineering}\\
          \href{http://www.unical.it/}{University of Calabria}\hfill\textit{Cosenza, IT}\\
          % Received Dec 11, 2007
          \begin{tabular}{lp{5cm}}
            \textit{Final degree mark:} &  110 (out of 110) cum laude\\
            \ifthenelse{\boolean{extended}}{
              \textit{Thesis Topic:}      &  Clustering based on summarization
                techniques on multidimensional data\\
              \textit{Adviser:}           &  Prof. Filippo Furfaro
                (\href{http://www.deis.unical.it}{DEIS Dep.}) \\
              &  Prof. Massimiliano Mazzeo
                (\href{http://www.deis.unical.it}{DEIS Dep.})\\
              \textit{Main subjects:}     &  Database, Software Engineering,
                Operating Systems, Informatics Systems, Information Theory\\
            }
          \end{tabular}
          \ifthenelse{\boolean{extended}}{
            \hyperlink{iit}{\hfill | \footnotesize Detailed List of Exams} \\
          }
        \end{cvlist}
      \end{minipage}
      \hspace{1em}
      \begin{minipage}[t]{0.33\textwidth}
      % Reduce the space between label and text
      \setlength{\cvlabelwidth}{0.5em}
      \begin{cvlist}{Skills}
        \item[\textbf{Languages}:] Java, Python, Bash, UML
        \item[\textbf{Unix Sytems}:] Arch Linux, Red Hat, Debian
        \item[\textbf{Cloud Computing}:] Amazon Web Services, Digital Ocean
        \item[\textbf{Revision control}] Git, SVN
        \item[\textbf{Digital typesetting}:] \TeX, \LaTeX
      \end{cvlist}
      \begin{cvlist}{Certificates}
        \item[\textbullet] AWS Certified Solutions Architect - Associate
        \item[\textbullet] Preliminary English Test, University of Cambridg
          (ESOL) Examinations, Level B1.
        \item[\textbullet] Intensive Course of Spanish, Polytechnic University
          of Valencia, Level A2.
      \end{cvlist}
      \begin{cvlist}{Courses}
        \item[2012] \href{https://class.coursera.org/progfun-2012-001/class/index}{Functional Programming Principles in Scala Open Course, Coursera}
        \item[2012] \href{https://www.coursera.org/saas/class/index}{Software Engineering for SaaS, Coursera}
        \item[2012] \href{https://class.coursera.org/algo/class/index}{Design and Analysis of Algorithms I, Coursera}
        \item[2011] \href{http://www.ml-class.org/course/class/index}{Machine Learning, Coursera}
        \item[2011] \href{http://www.db-class.org/course/class/index}{Introduction to Databases, Coursera}
        \item[2011] \href{http://www.cfp.upv.es/formacion-permanente/index/index.jsp}{Development of Web Information Systems based on Java Server Faces, J2EE, Ajax and Hibernate, Polytechnic University of Valencia}
      \end{cvlist}
      \begin{cvlist}{Projects}
        \item[\textbullet] Creator of popular open-source projects: \href{https://github.com/fsquillace/junest}{JuNest}, \href{https://github.com/pearl-core/pearl}{Pearl}
      \end{cvlist}
      \begin{cvlist}{Links}
        \item[\textbullet] \footnotesize{https://linkedin.com/in/filipposquillace}
        \item[\textbullet] \footnotesize{https://github.com/fsquillace}
      \end{cvlist}
    \end{minipage}
  \end{cv}
  %Footer
  \begin{center}
    \footnotesize{Last updated: \today}
  \end{center}
  \footnotetext{Additional information can be found in the \href{https://linkedin.com/in/filipposquillace}{LinkedIn} account.}
\end{document}